### 2018-05-29 latex/sc18/appendix.tex
3D weak scaling in appendix

>>>>

\begin{figure}
\begin{tikzpicture}
\renewcommand{\datafile}{data/wk_3D_syn2_scale_pgf.dat}
\renewcommand{\numiterations}{10}
\weakthreeDtrue
\breakdownplot
%\labels
\end{tikzpicture}
\caption{Weak scaling of 3D synthetic tensors with (D) and without (N) the use of dimension trees.  The tensor and processor grid dimensions are $128k\times 128k\times 128k$ and $k\times k\times k$ for $k\in\{1,2,3,4\}$, and the rank is fixed at 32.  The reported times are per iteration.}
\label{fig:weaksynthetic3D}
\end{figure}
